HTW Model2

### 2024-03-23 Model/pdf_test2.qmd
added e2 & e3 brms error model tables. Reorganized plots

---
title: HTW Model2
author: Thomas Gorman
pdf-engine: pdflatex
execute: 
  warning: false
  eval: false
  include: false
  echo: false
format:
  #html: default
  pdf: 
    header-includes:
    - '\KOMAoption{captions}{tableheading}'
    - '\usepackage{float}'
    - '\floatplacement{table}{H}'
    - '\usepackage{tabularx}'
    - '\usepackage{etoolbox}'
---

@@

```{r}
#| label: tbl-metricsvoters
#| tbl-cap: "Average metrics across the 10"

wide_data <- e23_tab %>%
  pivot_wider(
    names_from = c(Exp, condit),
    values_from = mean_error,
    names_sep = "_"
  )

# Create a gt table with the wider data
gt_table <- wide_data %>%
  gt() %>%
  tab_header(
    title = "Mean Error by Model and Condition",
    subtitle = "Comparison of ALM and EXAM Models across Different Fit Methods"
  ) %>%
  fmt_number(
    columns = everything(),
    decimals = 1  # Adjust the number of decimal places as needed
  ) %>%
  cols_label(
    `Task Stage` = "Task Stage"
  ) %>%
  tab_spanner_delim(delim = "_") %>%
  tab_style(
    style = cell_fill(color = "gray95"),
    locations = cells_body(columns = TRUE, rows = TRUE)
  ) %>%
  tab_style(
    style = cell_borders(sides = "top", color = "black", weight = px(2)),
    locations = cells_column_labels()
  ) %>%
  tab_style(
    style = cell_text(align = "left"),
    locations = cells_column_labels(columns = TRUE)
  ) %>%
  tab_options(
    column_labels.font.size = "small",
    heading.title.font.size = "large",
    heading.subtitle.font.size = "medium",
     quarto.disable_processing = TRUE
  )

# Print the table
print(gt_table)
```

@@

wide_data <- e23_tab %>%
  pivot_wider(
    names_from = c(Exp, Model, condit),
    values_from = mean_error,
    names_glue = "{Exp}_{Model}_{condit}"
  ) %>%
  arrange(Fit_Method, `Task Stage`)

gt_table <- wide_data %>%
  gt() %>%
  tab_header(
    title = "Mean Error by Fit Method, Task Stage, and Experiment"
  ) %>%
  cols_move_to_start(columns = c(`Task Stage`)) %>%
  cols_label(
    `Task Stage` = "Task Stage"
  ) %>%
  fmt_number(
    columns = matches("E2|E3"),
    decimals = 2
  ) %>%
  tab_spanner_delim(delim = "_") %>%
  tab_options(
    column_labels.font.size = 12,
    heading.title.font.size = 12,
    table.font.size = 12,
    table.font.names = "Times New Roman",
    table.width = pct(100),
    table.border.top.style = "solid",
    table.border.top.width = px(2),
    table.border.bottom.style = "solid",
    table.border.bottom.width = px(2),
    column_labels.border.top.style = "solid",
    column_labels.border.top.width = px(2),
    column_labels.border.bottom.style = "solid",
    column_labels.border.bottom.width = px(1),
    quarto.disable_processing = TRUE
  ) %>%
  tab_footnote(
    footnote = "Note. Mean errors are calculated as the absolute difference between the predicted and actual values.",
    locations = cells_title(groups = "title")
  ) # %>% opt_align_table_header(align = "left")

gt_table
# gtsave(gt_table, "table.png")
```

```{r}
wide_data <- e23_tab %>%
  pivot_wider(
    names_from = c(Exp, Model, condit),
    values_from = mean_error,
    names_glue = "{Exp}_{Model}_{condit}"
  ) %>%
  arrange(Fit_Method, `Task Stage`)  # Sort for clarity

@@

```{r}
wide_data <- e23_tab %>%
  pivot_wider(
    names_from = c(Exp, Model, condit),
    values_from = mean_error,
    names_glue = "{Exp}_{Model}_{condit}"
  ) %>%
  arrange(Fit_Method, `Task Stage`)  # Sort for clarity

# Create a gt table with the wider data
gt_table <- wide_data %>%
  gt() %>%
  tab_header(
    title = "Mean Error by Fit Method, Task Stage, and Experiment",
    subtitle = "Comparison across Conditions and Models"
  ) %>%
  cols_move_to_start(columns = c(`Task Stage`)) %>% # Move Task Stage column to the start
  cols_label(
    `Task Stage` = "Task Stage"
  ) %>%
  fmt_number(
    columns = matches("E2|E3"),
    decimals = 1  # Adjust the number of decimal places as needed
  ) %>%
  tab_spanner_delim(delim = "_") %>%
  tab_style(
    style = cell_fill(color = "gray95"),
    locations = cells_body(columns = TRUE, rows = TRUE)
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "gray90"),
    locations = cells_body(columns = TRUE, rows = TRUE)
  ) %>%
  tab_style(
    style = cell_borders(sides = "top", color = "black", weight = px(1)),
    locations = cells_column_labels()
  ) %>%
  tab_options(
    column_labels.font.size = 10,
    heading.title.font.size = 14,
    heading.subtitle.font.size = 12,
    table.width = pct(100), # Set the table width to 100% of the container
    table.font.size = 10
  ) %>%
  tab_footnote(
    footnote = "Note: Mean errors are calculated as the absolute difference between the predicted and actual values.",
    locations = cells_title(groups = "subtitle")
  )

# Print the table for HTML output
#as_raw_html(gt_table)

# For PDF output, you might need to save the table as an image and then include it
# This is a workaround due to the limited support for HTML tables in PDF
#gtsave(gt_table, "table_for_pdf.png", path = "path_to_directory")

@@

gt_table <- wide_data %>%
  gt() %>%
  tab_header(
    title = "Mean Error by Fit Method, Task Stage, and Experiment",
    subtitle = "Comparison across Conditions and Models"
  ) %>%
  cols_move_to_start(columns = c(`Task Stage`)) %>% # Move Task Stage column to the start
  cols_label(
    `Task Stage` = "Task Stage"
  ) %>%
  fmt_number(
    columns = matches("E2|E3"),
    decimals = 1  # Adjust the number of decimal places as needed
  ) %>%
  tab_spanner_delim(delim = "_") %>%
  tab_style(
    style = cell_fill(color = "gray95"),
    locations = cells_body(columns = everything(), rows = TRUE)
  ) %>%
  tab_style(
    style = cell_borders(sides = c("left", "right", "top", "bottom"), color = "gray90"),
    locations = cells_body(columns = everything(), rows = TRUE)
  ) %>%
  tab_style(
    style = cell_borders(sides = "top", color = "black", weight = px(1)),
    locations = cells_column_labels()
  ) %>%
  tab_options(
    column_labels.font.size = 10,
    heading.title.font.size = 14,
    heading.subtitle.font.size = 12,
    table.width = pct(100), # Set the table width to 100% of the container
    table.font.size = 10,
    quarto.disable_processing = TRUE
  ) %>%
  tab_footnote(
    footnote = "Note: Mean errors are calculated as the absolute difference between the predicted and actual values.",
    locations = cells_title(groups = "subtitle")
  )
gt_table
```

```{r}
e23_tab_wide <- e23_tab %>%
  pivot_wider(
    id_cols = c(Fit_Method, `Task Stage`, Exp),
    names_from = c(condit, Model),
    values_from = mean_error
  )

# Reorder columns
e23_tab_wide <- e23_tab_wide %>%
  select(Fit_Method, Exp, contains("Varied"), contains("Constant"), `Task Stage`)

# Rename columns
e23_tab_wide <- e23_tab_wide %>%
  rename_with(~ str_replace(., "_Varied_", " (Varied) "), starts_with("Varied")) %>%
  rename_with(~ str_replace(., "_Constant_", " (Constant) "), starts_with("Constant")) %>%
  rename_with(~ str_replace(., "_ALM", " (ALM)"), ends_with("ALM")) %>%
  rename_with(~ str_replace(., "_EXAM", " (EXAM)"), ends_with("EXAM"))

# Create gt table
gt_table <- gt(e23_tab_wide) %>%
  tab_header(
    title = md("**Table 1.** Mean Error by Fit Method, Experiment, and Condition"),
    subtitle = md("Note. ALM = additive linear model, EXAM = exam score model.")
  ) %>%
  tab_options(
    column_labels.hidden = FALSE,
    heading.title.font.size = px(16),
    heading.subtitle.font.size = px(12),
    table.font.size = px(10)
  ) %>%
  fmt_number(
    columns = everything(),
    decimals = 1
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(columns = Fit_Method)
  ) %>%
  tab_style(
    style = cell_text(align = "left"),
    locations = cells_body(columns = c(Fit_Method, Exp, contains("Varied"), contains("Constant"), `Task Stage`))
  ) %>%
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_body(columns = starts_with("Varied"), starts_with("Constant"))
  ) %>%
  tab_spanner(
    label = md("**Fit Method**"),
    columns = Fit_Method
  ) %>%
  tab_spanner(
    label = md("**Experiment**"),
    columns = c(Exp, contains("Varied"), contains("Constant"))
  ) %>%
  tab_spanner(
    label = md("**Condition**"),
    columns = starts_with("Varied")
  ) %>%
  tab_spanner(
    label = md(""),
    columns = starts_with("Constant")
  ) %>%
  tab_spanner(
    label = md("**Task Stage**"),
    columns = `Task Stage`
  ) %>%
  cols_hide(columns = Fit_Method) %>%
  cols_label(
    Fit_Method = "",
    `Task Stage` = "Task Stage"
  )

# Print table
gt_table
```

e23_tab_wide <- e23_tab %>%
  pivot_wider(
    id_cols = c(Fit_Method, `Task Stage`, Exp),
    names_from = c(condit, Model),
    values_from = mean_error
  )

# Rename columns
e23_tab_wide <- e23_tab_wide %>%
  rename_with(~ str_replace(., "_Constant_", " (Constant) "), starts_with("Constant")) %>%
  rename_with(~ str_replace(., "_Varied_", " (Varied) "), starts_with("Varied")) %>%
  rename_with(~ str_replace(., "_ALM", " (ALM)"), ends_with("ALM")) %>%
  rename_with(~ str_replace(., "_EXAM", " (EXAM)"), ends_with("EXAM"))

# Create gt table
gt_table <- gt(e23_tab_wide) %>%
  tab_header(
    title = md("**Table 1.**"),
    subtitle = md("An example of a gt table with e23_tab data")
  ) %>%
  tab_options(
    column_labels.hidden = FALSE,
    heading.title.font.size = px(16),
    heading.subtitle.font.size = px(12),
     quarto.disable_processing = TRUE
  ) %>%
  fmt_number(
    columns = everything(),
    decimals = 1
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold"),
      cell_fill(color = "lightgray")
    ),
    locations = cells_stub()
  ) %>%
  tab_style(
    style = cell_text(align = "left"),
    locations = cells_body(columns = everything())
  ) %>%
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_body(columns = starts_with("Constant"), starts_with("Varied"))
  )

# Print table
gt_table
```

```{r}
e23_tab_wide <- e23_tab %>%
  pivot_wider(
    id_cols = c(Fit_Method, `Task Stage`, Exp),
    names_from = c(condit, Model),
    values_from = mean_error
  )

# Reorder columns
e23_tab_wide <- e23_tab_wide %>%
  select(Fit_Method, `Task Stage`, Exp, contains("Varied"), contains("Constant"))

# Rename columns
e23_tab_wide <- e23_tab_wide %>%
  rename_with(~ str_replace(., "_Varied_", " (Varied) "), starts_with("Varied")) %>%
  rename_with(~ str_replace(., "_Constant_", " (Constant) "), starts_with("Constant")) %>%
  rename_with(~ str_replace(., "_ALM", " (ALM)"), ends_with("ALM")) %>%
  rename_with(~ str_replace(., "_EXAM", " (EXAM)"), ends_with("EXAM"))

# Create gt table
gt_table <- gt(e23_tab_wide) %>%
  tab_header(
    title = md("**Table 1.**"),
    subtitle = md("An example of a gt table with e23_tab data")
  ) %>%
  tab_options(
    column_labels.hidden = FALSE,
    heading.title.font.size = px(16),
    heading.subtitle.font.size = px(12)
  ) %>%
  fmt_number(
    columns = everything(),
    decimals = 1
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold"),
      cell_fill(color = "lightgray")
    ),
    locations = cells_stub()
  ) %>%
  tab_style(
    style = cell_text(align = "left"),
    locations = cells_body(columns = everything())
  ) %>%
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_body(columns = starts_with("Varied"), starts_with("Constant"))
  )

# Print table
gt_table

```{r}
#| label: "potential2"
#| tbl-cap: "this one has potential2"

#| 
wide_data <- e23_tab %>%
  pivot_wider(
    names_from = c(Exp, Model, condit),
    values_from = mean_error,
    names_glue = "{Exp}_{Model}_{condit}"
  ) %>%
  arrange(Fit_Method, `Task Stage`)  # Sort for clarity

# Create a gt table with the wider data
gt_table <- wide_data %>%
  gt() %>%
  tab_header(
    title = "Mean Error by Fit Method, Task Stage, and Experiment",
    subtitle = "Comparison across Conditions and Models"
  ) %>%
  cols_move_to_start(columns = c(`Task Stage`)) %>% # Move Task Stage column to the start
  fmt_number(
    columns = matches("E2|E3"),
    decimals = 1  # Adjust the number of decimal places as needed
  ) %>%
  cols_label(
    `Task Stage` = md("**Task Stage**")
  ) %>%
  tab_spanner_delim(delim = "_") %>%
  tab_spanner(
    label = md("**Fit Method**"),
    columns = vars(Fit_Method)
  ) %>%
  tab_style(
    style = cell_fill(color = "gray95"),
    locations = cells_body(columns = TRUE, rows = TRUE)
  ) %>%
  tab_style(
    style = cell_borders(sides = "top", color = "black", weight = px(2)),
    locations = cells_column_labels()
  ) %>%
  tab_options(
    column_labels.font.size = 10,
    heading.title.font.size = 14,
    heading.subtitle.font.size = 12,
    table.width = pct(100)  # Set the table width to 100% of the container

  ) %>%
  tab_footnote(
    footnote = "Note: All values represent mean errors.",
    locations = cells_column_labels(columns = TRUE)
  )

# Print the table
print(gt_table)
```

```{r}
#| label: tbl-metricsvoters222
#| tbl-cap: "this one has potential"

wide_data <- e23_tab %>%
  pivot_wider(
    names_from = c(Model, condit),
    values_from = mean_error,
    names_sep = "_"
  ) %>%
  arrange(Fit_Method, `Task Stage`, Exp)  # Sorting the data can help with clarity in presentation

# Create a gt table with the wider data
gt_table <- wide_data %>%
  gt() %>%
  tab_header(
    title = "Mean Error by Fit Method, Task Stage, and Experiment",
    subtitle = "Comparison across Conditions and Models"
  ) %>%
  fmt_number(
    columns = matches("ALM_|EXAM_"),
    decimals = 1  # Adjust the number of decimal places as needed
  ) %>%
  tab_spanner_delim(delim = "_") %>%
  tab_style(
    style = cell_fill(color = "gray95"),
    locations = cells_body(columns = TRUE, rows = TRUE)
  ) %>%
  tab_style(
    style = cell_borders(sides = "top", color = "black", weight = px(2)),
    locations = cells_column_labels()
  ) %>%
  tab_options(
    column_labels.font.size = "small",
    heading.title.font.size = "large",
    heading.subtitle.font.size = "medium",
    table.width = pct(100), # Set the table width to 100% of the container,
    quarto.disable_processing = TRUE
  )

# Print the table
print(gt_table)
```

```{r}
#| label: tbl-potential1
#| tbl-cap: "this one has even more potential"

# Create a gt table with the wider data
gt_table <- wide_data %>%
  gt() %>%
  tab_header(
    title = "Mean Error by Fit Method, Task Stage, and Experiment",
    subtitle = "Comparison across Conditions and Models"
  ) %>%
  cols_move_to_start(columns = c(`Task Stage`)) %>% # Move Task Stage column to the start
  cols_label(
    `Task Stage` = "Task Stage"
  ) %>%
  fmt_number(
    columns = matches("E2|E3"),
    decimals = 1  # Adjust the number of decimal places as needed
  ) %>%
  tab_spanner_delim(delim = "_") %>%
  tab_style(
    style = cell_fill(color = "gray95"),
    locations = cells_body(columns = TRUE, rows = TRUE)
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "gray90"),
    locations = cells_body(columns = TRUE, rows = TRUE)
  ) %>%
  tab_style(
    style = cell_borders(sides = "top", color = "black", weight = px(1)),
    locations = cells_column_labels()
  ) %>%
  tab_options(
    column_labels.font.size = 10,
    quarto.disable_processing = TRUE,
    heading.title.font.size = 14,
    heading.subtitle.font.size = 12,
    table.width = pct(100), # Set the table width to 100% of the container
    table.font.size = 10
  ) %>%
  tab_footnote(
    footnote = "Note: Mean errors are calculated as the absolute difference between the predicted and actual values.",
    locations = cells_title(groups = "subtitle")
  )

# Print the table
print(gt_table)
```

# Load necessary packages
pacman::p_load(dplyr, tidyr, gt)

# Pivot the data wider
e23_tab_wide <- e23_tab %>%
  pivot_wider(
    id_cols = c(Fit_Method, Model, `Task Stage`),
    names_from = c(condit, Exp),
    values_from = mean_error
  )

# Rename columns
e23_tab_wide <- e23_tab_wide %>%
  rename_with(~ str_replace(., "_Constant", " (Constant)"), starts_with("Constant")) %>%
  rename_with(~ str_replace(., "_Varied", " (Varied)"), starts_with("Varied")) %>%
  rename_with(~ str_replace(., "_E2", " (E2)"), ends_with("E2")) %>%
  rename_with(~ str_replace(., "_E3", " (E3)"), ends_with("E3"))

# Create gt table
gt_table <- gt(e23_tab_wide) %>%
  tab_header(
    title = md("**Table 1.**"),
    subtitle = md("An example of a gt table with e23_tab data")
  ) %>%
  tab_options(
    column_labels.hidden = FALSE,
    heading.title.font.size = px(16),
    heading.subtitle.font.size = px(12),
     quarto.disable_processing = TRUE
  ) %>%
  fmt_number(
    columns = everything(),
    decimals = 1
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold"),
      cell_fill(color = "lightgray")
    ),
    locations = cells_stub()
  ) %>%
  tab_style(
    style = cell_text(align = "left"),
    locations = cells_body(columns = everything())
  ) %>%
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_body(columns = starts_with("Constant"), starts_with("Varied"))
  )

# Print table
gt_table
```

e23_tab %>%
  gt() %>%
  tab_header(
    title = "Mean Error by Model and Condition",
    subtitle = "Comparison of ALM and EXAM Models across Different Fit Methods"
  ) %>%
  fmt_number(
    columns = c("mean_error"),
    decimals = 1  # Adjust the number of decimal places as needed
  ) %>%
  cols_label(
    mean_error = "Mean Error",
    `Task Stage` = "Task Stage",
    Exp = "Experiment"
  ) %>%
  # The below spanner code should be adjusted if `Task Stage` and `Exp` are not directly next to each other
  tab_spanner(
    label = "Details",
    columns = c(`Task Stage`, Exp)
  ) %>%
  tab_style(
    style = cell_fill(color = "gray95"),
    locations = cells_body(columns = TRUE, rows = TRUE)
  ) %>%
  tab_style(
    style = cell_borders(sides = "top", color = "black", weight = px(2)),
    locations = cells_column_labels()
  ) %>%
  tab_style(
    style = cell_text(align = "left"),
    locations = cells_column_labels(columns = TRUE)
  ) %>%
  tab_options(
    column_labels.font.size = "small",
    heading.title.font.size = "large",
    heading.subtitle.font.size = "medium",
     quarto.disable_processing = TRUE
  )
```

e23_tab %>%
  gt() %>%
  tab_header(
    title = "Mean Error for Different Fitting Methods and Models",
    subtitle = "Results from Experiments E2 and E3"
  ) %>%
  cols_label(
    Fit_Method = md("Fitting Method"),
    Model = md("Model"),
    condit = md("Condition"),
    mean_error = md("Mean Error"),
    `Task Stage` = md("Task Stage"),
    Exp = md("Experiment")
  ) %>%
  tab_source_note(
    source_note = "Data source: e23_tab"
  ) %>%
  tab_footnote(
    footnote = "Constant and Varied refer to the conditions of the experiment.",
    locations = cells_body(columns = condit)
  ) %>%
  fmt_number(
    columns = mean_error,
    decimals = 1
  ) %>%
  cols_align(
    align = "left",
    columns = c(Fit_Method, Model, condit, `Task Stage`, Exp)
  ) %>%
  cols_align(
    align = "center",
    columns = mean_error
  )  %>%
    tab_options(
     quarto.disable_processing = TRUE
  )
```

>>>>

---
title: HTW Model2
author: Thomas Gorman
pdf-engine: pdflatex
execute: 
  warning: false
  eval: true
  include: true
  echo: false
format:
  html: default
  pdf: 
    header-includes:
    - '\KOMAoption{captions}{tableheading}'
    - '\usepackage{float}'
    - '\floatplacement{table}{H}'
    - '\usepackage{tabularx}'
    - '\usepackage{etoolbox}'
---

@@

@@

## 2nd GT

```{r}
#| label: tbl-pdf-html2
#| tbl-cap: "Mean Error by Fit Method, Task Stage, and Experiment"

@@

@@

# Assuming e23_tab is already created and is in the environment

# Pivot the data to spread 'condit' and 'Model' levels into columns
wide_data <- e23_tab %>%
  pivot_wider(
    names_from = c(Exp, Model, condit),
    values_from = mean_error,
    names_glue = "{Exp}_{Model}_{condit}"
  ) %>%
  arrange(Fit_Method, `Task Stage`)  # Sort for clarity

# Create a gt table with the wider data
gt_table <- wide_data %>%
  gt() %>%
  tab_header(
    title = "Mean Error by Fit Method, Task Stage, and Experiment",
    subtitle = "Comparison across Conditions and Models"
  ) %>%
  cols_move_to_start(columns = c(`Task Stage`)) %>% # Move Task Stage column to the start
  cols_label(
    `Task Stage` = "Task Stage"
  ) %>%
  fmt_number(
    columns = matches("E2|E3"),
    decimals = 1  # Adjust the number of decimal places as needed
  ) %>%
  tab_spanner_delim(delim = "_") %>%
  tab_style(
    style = cell_fill(color = "gray95"),
    locations = cells_body(columns = TRUE, rows = TRUE)
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "gray90"),
    locations = cells_body(columns = TRUE, rows = TRUE)
  ) %>%
  tab_style(
    style = cell_borders(sides = "top", color = "black", weight = px(1)),
    locations = cells_column_labels()
  ) %>%
  tab_options(
    column_labels.font.size = 10,
    heading.title.font.size = 14,
    heading.subtitle.font.size = 12,
    table.width = pct(100), # Set the table width to 100% of the container
    table.font.size = 10,
    table.font.names = "Arial", # Specify a font that is available in both HTML and PDF
    data_row.padding = px(3), # Adjust padding for better rendering in PDF
    source_notes.font.size = 8 # Adjust font size for source notes
  ) %>%
  tab_footnote(
    footnote = "Note: Mean errors are calculated as the absolute difference between the predicted and actual values.",
    locations = cells_title(groups = "subtitle")
  )

#gt_table
# Save the table as an image file
# gtsave(gt_table, "table.png", expand = 10, vwidth = 1000, vheight = 500)
```
